dendro

### 2017-05-19 analysis/test-bai.Rmd
update

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
# library("detrendeR")
library("pander")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
```

@@

```{r, echo=FALSE}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

@@

# Get only focal trees, and only selected variables 
ft <- compete %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno') %>% 
  dplyr::select(id_focal, loc, dn_mm, height_cm)

# Set levels of eleveation 
sj_lowcode  <- paste0('A', str_pad(1:10, 2, pad='0'))
sj_highcode <- paste0('A', 11:20)
ca_lowcode <- c(paste0('B', str_pad(1:10, 2, pad='0')),
            paste0('B', 26:30))
ca_highcode <- paste0('B', 11:25)

ft <- ft %>% 
  mutate(elev = as.factor(
    ifelse(id_focal %in% sj_lowcode, 'Low',
                       ifelse(id_focal %in% sj_highcode, 'High',
                              ifelse(id_focal %in% ca_lowcode, 'Low', 'High'))))) %>%
  mutate(site = as.factor(paste0(loc, '_', elev)))
```

* Crear dataframes `rwl` por cada sitio CA_High, CA_Low, SJ_High. SJ_Low (:red_circle: mejorar la forma de hacerlo)

```{r}
# Create subset to compare between sites 
caL <- ca[,c("SNB0101","SNB0102","SNB0201","SNB0202","SNB0301","SNB0302","SNB0401","SNB0402","SNB0501","SNB0502g",
             "SNB0601","SNB0602","SNB0701","SNB0702g","SNB0801g","SNB0802g","SNB0901g","SNB0902","SNB1001","SNB1002",
             "SNB2601","SNB2602","SNB2701","SNB2702g","SNB2801","SNB2802","SNB2901","SNB2902","SNB3001","SNB3002")]

caH <- ca[, c("SNB1101","SNB1102","SNB1201","SNB1202","SNB1301","SNB1302","SNB1401","SNB1402","SNB1501","SNB1502",
              "SNB1601","SNB1602","SNB1701","SNB1702","SNB1801","SNB1802","SNB1901","SNB1902","SNB2001","SNB2002g",
              "SNB2101","SNB2102","SNB2201g","SNB2202g","SNB2301g","SNB2302","SNB2401","SNB2402","SNB2501","SNB2502")]

sjL <- sj[, c("SNA0101","SNA0102","SNA0201","SNA0202","SNA0301","SNA0302","SNA0401","SNA0402","SNA0501","SNA0502",
              "SNA0601","SNA0602","SNA0603","SNA0701","SNA0702","SNA0801","SNA0802","SNA0901","SNA0902","SNA0903",
              "SNA1001","SNA1002","SNA1003")]
sjH <- sj[, c("SNA1101","SNA1102","SNA1103","SNA1201","SNA1202","SNA1203","SNA1301","SNA1302","SNA1303","SNA1401",
              "SNA1402","SNA1501","SNA1502","SNA1601","SNA1602","SNA1701","SNA1702","SNA1703","SNA1801","SNA1802",
              "SNA1901","SNA1902","SNA2001","SNA2003","SNA2002")]
```

@@

# Aggregate RW by tree 
* Agregar valores medios de RW por loc (obtenemos sj_tree / ca_tree) o por site (sjL_tree, sjH_tree / caL_tree, caH_tree) 
* ver fun

```{r}
sj_tree <- rw_byTree(sj)
ca_tree <- rw_byTree(ca)

sjL_tree <- rw_byTree(sjL)
sjH_tree <- rw_byTree(sjH)
caL_tree <- rw_byTree(caL)
caH_tree <- rw_byTree(caH)
```

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
library("detrendeR")
library("pander")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
```

@@

```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

* Crear dataframes `rwl` por cada sitio CA_High, CA_Low, SJ_High. SJ_Low (:red_circle: mejorar la forma de hacerlo)
    * :red_circle: ojo he cambiado los nombres de las series en SJ y en CA

```{r}
# Replace SNA by SJ and SNB by CA
names(ca) <- stringr::str_replace(names(ca), "SNB", "CA") 
names(sj) <- stringr::str_replace(names(sj), "SNA", "SJ")

# Remove g in name of some cores of CA. 
names(ca) <- stringr::str_replace(names(ca), "g", "")
```

```{r}
# Create subset to compare between sites 
caL <- ca[,c("CA0101","CA0102","CA0201","CA0202","CA0301","CA0302","CA0401","CA0402","CA0501","CA0502",
             "CA0601","CA0602","CA0701","CA0702","CA0801","CA0802","CA0901","CA0902","CA1001","CA1002",
             "CA2601","CA2602","CA2701","CA2702","CA2801","CA2802","CA2901","CA2902","CA3001","CA3002")] 
caH <- ca[, c("CA1101","CA1102","CA1201","CA1202","CA1301","CA1302","CA1401","CA1402","CA1501","CA1502",
              "CA1601","CA1602","CA1701","CA1702","CA1801","CA1802","CA1901","CA1902","CA2001","CA2002",
              "CA2101","CA2102","CA2201","CA2202","CA2301","CA2302","CA2401","CA2402","CA2501","CA2502")]

sjL <- sj[, c("SJ0101","SJ0102","SJ0201","SJ0202","SJ0301","SJ0302","SJ0401","SJ0402","SJ0501","SJ0502",
              "SJ0601","SJ0602","SJ0603","SJ0701","SJ0702","SJ0801","SJ0802","SJ0901","SJ0902","SJ0903",
              "SJ1001","SJ1002","SJ1003")]
sjH <- sj[, c("SJ1101","SJ1102","SJ1103","SJ1201","SJ1202","SJ1203","SJ1301","SJ1302","SJ1303","SJ1401",
              "SJ1402","SJ1501","SJ1502","SJ1601","SJ1602","SJ1701","SJ1702","SJ1703","SJ1801","SJ1802",
              "SJ1901","SJ1902","SJ2001","SJ2003","SJ2002")]
```

@@

# Change name focal according to loc
compete <- compete %>% 
  mutate(id_focalLoc = stringr::str_replace_all(id_focal, c("A" = "SJ", "B" = "CA")))

# Get only focal trees, and only selected variables 
ft <- compete %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno') %>% 
  dplyr::select(id_focal, id_focalLoc, loc, dn_mm, height_cm)

# Set levels of eleveation 
sj_lowcode  <- paste0('SJ', str_pad(1:10, 2, pad='0'))
sj_highcode <- paste0('SJ', 11:20)
ca_lowcode <- c(paste0('CA', str_pad(1:10, 2, pad='0')),
            paste0('CA', 26:30))
ca_highcode <- paste0('CA', 11:25)

ft <- ft %>% 
  mutate(elev = as.factor(
    ifelse(id_focalLoc %in% sj_lowcode, 'Low',
                       ifelse(id_focalLoc %in% sj_highcode, 'High',
                              ifelse(id_focalLoc %in% ca_lowcode, 'Low', 'High'))))) %>%
  mutate(site = as.factor(paste0(loc, '_', elev)))
```

* Crear dataframes `rwl` por cada sitio CA_High, CA_Low, SJ_High. SJ_Low (:red_circle: mejorar la forma de hacerlo)
    * :red_circle: ojo he cambiado los nombres de las series en SJ y en CA

@@

# Aggregate RW by tree

* Agregar valores medios de RW por loc (obtenemos sj_tree / ca_tree) o por site (sjL_tree, sjH_tree / caL_tree, caH_tree) 
* ver fun rw_byTree o utilizar treeMean (dplR)

```{r}
# Remember snc = structure of core name SJ0101 (site | tree | core)
sj_tree <- rw_byTree(sj, snc =c(2,2,2))
ca_tree <- rw_byTree(ca, snc =c(2,2,2))

sjL_tree <- rw_byTree(sjL, snc =c(2,2,2))
sjH_tree <- rw_byTree(sjH, snc =c(2,2,2))
caL_tree <- rw_byTree(caL, snc =c(2,2,2))
caH_tree <- rw_byTree(caH, snc =c(2,2,2))

# Si decido usar treeMean debería ser (solo un ejemplo)
# ids_sj <- read.ids(sj, stc = c(2, 2, 2))
# sj_meantree <- treeMean(sj, ids = ids_sj,  na.rm=TRUE)
```
